Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-22 journal/article.tex
Work in progress

@@

@@

>>>>

Many cases highlighted how people were engaged broadly in the organization.
One of the lessons learned presented was that it is important to involve all
stakeholders to gain acceptance in the transformation [P4, P31]. The transition
team made an effort to engage people by both inviting to give feedback online
and holding an extensive number of feedback meetings [P6, P22, P16]
Being inclusive towards everyone was seen as one of the key success factors in
the transformation [P16]. Inclusiveness will encourage people to participate and
use the new model visibly [P16].

\subsubsection{Have a change leading coalition}

Organizing a large number of people requires some management and leadership.
Similarly, transforming the way of working of a large group requires coordinaion
and leadership [P42, P31]. In addition to the leadership provided by coaches,
specific change leaders were also mentioned. Cases indicated the importance of
having spokespersons for the change [P3, P4, P31]. Cowan [P11] describes how one
person was strongly driving the transformation, and made an indisputable
contribution for transforming the organization. Also Maples [P31] describes how
the change and agile adoption was guided by one ``counselor'' [P31]. Other cases
described that the change was lead by a competent rollout team, which had
representatives from all parts of the organization [P16, P33]. Finally, the
responsibility of line and project managers to act as change leaders was
highlighted [P18].

@@

The formation and influence of agile communities had a significant impact on
transformation.

@@

* A success factor: Agile communities emerged
* Communities are commonly created in agile initiatives
[P3]

* There was an agile community which spawned eager followers
* The community shared experiences and advice
* The community emerged self-organized
[P12]

* Project managers were in a matrix structure
* The matrix enabled sharing of learnings and confirmation 
[P12]

* The organization is planning on establishing an agile CoP
[P30]

* The coaches built up an agile community
* There was online discussions, newsletters, and workshop events
[P41]

* The company has communities of practice, which are effective in raising awareness
  of engineering practices
[P42]

* The agile coach community is a driving force --> They achieved becomming a driving force
* The community created practices promoting the use of agile methods in the organization
[P47]

* A collective group is required to make chage in an organization
* Impediments may be too large for individuals to move
[P47]

S: Have an agile community
